Weather vanes and runaways: Bow shocks across the HR diagram

### 2018-06-26 papers/Papers1234/app-dust-wave.tex
Finish the figure caption for perpendicular B field

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/perp-bfield-dust-wave-inertia}
  \caption{Dust wave formed by action of radiation forces on grains
    that are tightly coupled to a uniform perpendicular magnetic
    field.}
  \label{fig:inertia-thB90}
\end{figure}

For \(\theta\B = \ang{90}\), the guiding center is forced to move at a
constant speed in the \(x\) direction, so that \(x = -v_\infty t\), while
the motion in the \(y\) direction obeys the ODE:
\begin{equation}
  \label{eq:ode-perp-bfield}
  \frac{d^2 Y}{d X^2} = \frac{Y}{2 \left( X^2 + Y^2\right)^{3/2}} \ ,
\end{equation}
where \(X = x / R\starstar\) and \(Y = y / R\starstar\).  We have been
unable to find an analytic solution to this equation, but a numerical
solution is shown in Figure~\ref{fig:inertia-thB90}.  When the impact
parameter is larger than \(b \sim R\starstar\), the trajectories are very
similar to in the non-magnetic case
(Fig.~\ref{fig:dust-trajectories}a).  As shown in
Figure~\ref{fig:inertia-thB90}b, the interaction of the grain with the
radiation field in this large-\(b\) regime can be approximated as an
impulsive acceleration of magnitude \(\sim b^{-2}\) and duration
\(\sim b\), producing a final \(y\) velocity of \(\sim b^{-1}\).  Since the
\(x\) velocity is constant, the total deflection angle is also of
order \(\sim b^{-1}\).  The overlap of the outgoing trajectories produces
a dense concentration of grains at the inner edge, which is roughly
parabolic in shape.  However, for \(b < R\starstar\) the remorseless
advance of the magnetic field does not allow the grains to slow down
and turn round, as they do in the non-magnetic and parallel-field
cases.  As a result, no dense shell forms in the apex region, but
instead there is a diffuse minimum in the density of grains around the
star due to the high grain velocities reached there.  This means that
the apparent morphology of a pure dust wave becomes very sensitive to
the radial dependence of the grain emissivity.  If this is
sufficiently steep, then the apex would coincide with the position of
the star, although in practice the presence of a wind-supported bow
shock, however small, will complicate the picture.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/perp-bfield-dust-wave-inertia}
  \caption{Dust wave formed by action of radiation forces on grains
    that are tightly coupled to a uniform perpendicular magnetic
    field.  (a)~Sample trajectories are shown by thin black lines and
    the resultant dust density distribution in grayscale.  Two
    parabolic fits to the inner edge of the dust wave in the wing
    region (\(y > R\starstar\)) are shown. The orange line shows a
    simultaneous fit to both wings, while the green line shows a fit
    to a single wing, in which the parabola apex is not constrained to
    lie on the axis.  The second fit has much smaller residuals,
    indicating that the overall dust wave shape is ``pointier'' than a
    parabola, but this is hard to quantify because the disappearance
    of the dense shell in the apex region makes it impossible to
    define \(R_0\) for the bow.  (b)~Trajectory parameters over a wide
    range of impact parameters, shown on a log--log scale. Distances
    are in units of \(R\starstar\), times in units of
    \(R\starstar / v_\infty\), velocities in units of \(v_\infty\), and
    accelerations in units of \(v_\infty^2 / R\starstar\). The grain's
    acceleration along the \(y\) axis has a maximum value,
    \(a_{\text{max}}\), which occurs at a position
    \(x(a_{\text{max}}), y(a_{\text{max}})\), just before the grain is
    swept past the star, with a duration (FWHM) of \(\Delta t\).  The
    grain's asymptotic \(y\) velocity is \(v_{\text{final}}\) and the
    fact that this closely tracks \(a_{\text{max}} \times \Delta t\) indicates
    that the majority of the acceleration occurs in a sharp impulse.
    The curves tend to straight lines at the right side of the graph,
    which gives the asymptotic scaling relations discussed in the
    text.}
  \label{fig:inertia-thB90}
\end{figure}

For \(\theta\B = \ang{90}\), the guiding center is forced to move at a
constant speed in the \(x\) direction, so that \(x = -v_\infty t\), while
the motion in the \(y\) direction obeys the ODE:
\begin{equation}
  \label{eq:ode-perp-bfield}
  \frac{d^2 y}{d x^2} = \tfrac12 R\starstar  \,
  y \, \bigl( x^2 + y^2\bigr)^{-3/2} \ .
\end{equation}
We have been unable to find an analytic solution to this equation, but
a numerical solution is shown in Figure~\ref{fig:inertia-thB90}.  When
the impact parameter is larger than \(b \sim R\starstar\), the
trajectories are very similar to in the non-magnetic case
(Fig.~\ref{fig:dust-trajectories}a).  As shown in
Figure~\ref{fig:inertia-thB90}b, the interaction of the grain with the
radiation field in this large-\(b\) regime can be approximated as an
impulsive acceleration of magnitude \(\sim b^{-2}\) and duration
\(\sim b\), producing a final \(y\) velocity of \(\sim b^{-1}\).  Since the
\(x\) velocity is constant, the total deflection angle is also of
order \(\sim b^{-1}\).  The overlap of the outgoing trajectories produces
a dense concentration of grains at the inner edge, which is roughly
parabolic in shape.  However, for \(b < R\starstar\) the remorseless
advance of the magnetic field does not allow the grains to slow down
and turn round, as they do in the non-magnetic and parallel-field
cases.  As a result, no dense shell forms in the apex region, but
instead there is a diffuse minimum in the density of grains around the
star due to the high grain velocities reached there.  This means that
the apparent morphology of a pure dust wave becomes very sensitive to
the radial dependence of the grain emissivity.  If this is
sufficiently steep, then the apex would coincide with the position of
the star, although in practice the presence of a wind-supported bow
shock, however small, will complicate the picture.
